---
title: "Iris Dataset analysis"
author: "Chan Mony Lach"
date: "29/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The beginning
Hello World!

I am far from being experienced in data science, therefore I figured I should start with one of the most common datasets in the world; the *IRIS* dataset.

This dataset is was commonly referred to in throughout my university courses as a means to introduce various machine learning/statistical concepts. 

Fortunately this dataset is already built into R, which makes it a suitable candidate for a beginner Exploratory Data Analysis (EDA). 

The dataset describes three classes of flowers:

 * Setosa
 * Versicolor
 * Virginica

As well as their sepal length/width and petal length/width. 
```{r cars}
iris_data <- iris
describe(iris)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
