---
title: "MT Cars Analysis"
author: "Chan Mony Lach"
date: "05/02/2020"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(ggplot2) #mtcars dataset part of ggplot2 package and visualisation
library(skimr) #to skim dataset
library(visdat)
library(MASS)
library(fitdistrplus)
library(logspline)
```

This will be the second installment of my portfolio. In this markdown document, I'll be analysing the mtcars dataset. 

> The mtcars data was extracted from the 1974 Motor Trend US magazine. It compares the fuel consumption and performance of thirty-two different automobiles based on ten different aspects of their design.

A snippet of this dataset is shown below: 
```{r}
head(mtcars)
```
Exploring the `?mtcars` function, I'm able to understand what each variable means. 

* mpg: Miles/(US) gallon
* cyl: Number of Cylinders
* disp: Displacement (cu.in.)
* hp: Gross Horsepower
* drat Rear axle ratio
* wt: Weight (1000lbs)
* qsec 1/4 mile time
* vs: Engine(0 = V-Shape, 1 = Straight)
* am: Transmission(0 = automatic, 1 = manual)
* gear: number of forward gears
* carb: Number of carburetors

To get a better understanding of the dataset, the `skim()` function will be used.
```{r}
skim(mtcars)
```
Under the *Variable type* table, the *n_missing* column shows a value of 0 for all variables of this dataset. This is good news as there is no missing data, and thus we can continue. However, this is to be expected, as this dataset was built into the immensly popular *ggplot2* package.

We also have 11 variables, which were listed previously. 

To visualise the different datatypes within the mtcars dataset we'll use the `vis_dat()` function from the `visdat` package

```{r}
vis_dat(mtcars)
```
This plot shows us that all the values in the dataset are of type numeric.
### Summary Statistics: 
```{r}
summary(mtcars)
```

## The Question
With all this information in hand, I would like to find out if **more horsepower results in a lower 1/4 mile time. **

To begin, the distribution of the required data should be visualised to get a feel for it. 

### Distribution of cars by Horsepower
```{r}
ggplot(mtcars, aes(hp)) + geom_histogram(binwidth = 10 )+ xlab('Horsepower') + ylab('No. of Cars') + ggtitle('Distribution of cars by Horsepower')
```

Though this looks like a right-skewed normal Gaussian distribution, I'll run some tests to see if there are any other candidates.

```{r, warnings = FALSE, messages=FALSE}
descdist(mtcars$hp, discrete=FALSE)
```

The kurtosis and squared skewness of the horsepower data appear as a blue bubble named "Observation". It appears that the closest distribution is the **Beta** distribution. 

This Shapiro-Wilk normality test also supports this statement:
```{r}
shapiro.test(mtcars$hp)
```
As the p-value is under 0.05, we have enough evidence to reject the null hypothesis that the data is fits a right-skewed normal distribution. 

### Distribution of cars by Quarter mile time
```{r}
ggplot(mtcars, aes(qsec)) + geom_histogram(binwidth = 0.5)+ xlab('Quarter Mile Time') + ylab('No. of Cars') + ggtitle('Distribution of cars by Quarter mile time')
```

This data appears to follow a Gaussian distribution. 

However, we'll perform a Shapiro-Wilk Normality test to see if this is true. 

```{r}
shapiro.test(mtcars$qsec)
```
With such a high p-value, we do not have enough evidence to reject the null hypothesis (distribution is Normal/Gaussian), therefore we cannot rule out that possibility. 

## Correlation between Quarter mile time and Horsepower.

```{r}
cor(mtcars$qsec, mtcars$hp)
```
This shows a strong negative correlation. 

##Plotting the data
```{r}
qplot(qsec, hp, data=mtcars)
```

This plot also shows a negative correlation with Horsepower and Quarter mile time. It appears that the more horsepower the car has, less time it takes in a quarter mile. 