---
title: "MT Cars Analysis"
author: "Chan Mony Lach"
date: "05/02/2020"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(ggplot2) #mtcars dataset part of ggplot2 package and visualisation
library(skimr) #to skim dataset
library(visdat)
```

This will be the second installment of my portfolio. In this markdown document, I'll be analysing the mtcars dataset. 

> The mtcars data was extracted from the 1974 Motor Trend US magazine. It compares the fuel consumption and performance of thirty-two different automobiles based on ten different aspects of their design.

A snippet of this dataset is shown below: 
```{r}
head(mtcars)
```
Exploring the `?mtcars` function, I'm able to understand what each variable means. 

* mpg: Miles/(US) gallon
* cyl: Number of Cylinders
* disp: Displacement (cu.in.)
* hp: Gross Horsepower
* drat Rear axle ratio
* wt: Weight (1000lbs)
* qsec 1/4 mile time
* vs: Engine(0 = V-Shape, 1 = Straight)
* am: Transmission(0 = automattic, 1 = manual)
* gear: number of forward gears
* carb: Number of carburetors

To get a better understanding of the dataset, the `skim()` function will be used.
```{r}
skim(mtcars)
```
Under the *Variable type* table, the *n_missing* column shows a value of 0 for all variables of this dataset. This is good news as there is no missing data, and thus we can continue. However, this is to be expected, as this dataset was built into the immensly popular *ggplot2* package.

To visualise the different datatypes within the mtcars dataset we'll use the `vis_dat()` function from the `visdat` package

```{r}
vis_dat(mtcars)
```

